---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# General overview

This repository contains all data, scripts and functions used to generate the Figure 1  of the paper "Three pathways to better recognize the expertise of Global South researchers" accepted for publication in npj Biodiversity journal.

In this study we brought secondary data from literature that evidence colonial imprints in academic expertise, and propose three pathways to reduce these biases.

# Repository structure

## Folders 

- data: contains all data needed to perform the analysis. 
    + `raw` contains all .txt files downloaded from Web of Science containing all records from 1000 top single author papers from different regions (defined accordingly World Bank - East Asia, Latin America, Middle and East Africa, South Asia, Sub-Sahara and USA-Canada) 
    + `processed` contains all .txt in `raw` after being processed using Bibliometrix package. Subfolders `*_citing_articles` contains information on articles that cited the top 1000 papers in raw for each region.

- doc: .doc documents containing the manuscript 

- output: contains all results, including the figures presented in the main text of this study. `res_boot_*.rds` are files containing results from rarefaction analysis described in `02_D_rarefaction_citation.Rmd`. Figure 1 and its components were generated using file `03_S_figure1-main-text.Rmd` 

- R: contains all Rmardown files with all analyctical procedures to run the analysis using literature data present in this study. `01_C_getting_processing.Rmd` contains all the querries used in Web of Science and the processing workflow used to extract the information needed in downstream analysis using Bibliometrix package. `02_D_GeoMarkers.Rmd` and `02_D_rarefaction_citation.Rmd` contains, respectively the scripts to get the number of geographical markers and rarefied citation values for each country in each World Bank region used in this study. `03_S_figure1-main-text.Rmd` is used to produce the Figure in the article.

# Downloading the repository

The user can download this repo to a local folder in your computer or clone it:

## downloading all files

```{r eval=FALSE, echo=TRUE}
download.file(url = "https://github.com/GabrielNakamura/Decolonizing_expertise/archive/main.zip", destfile = "Decolonizing_expertise.zip")
```


to unzip the .zip file in your computer type

```{r eval=FALSE,echo=TRUE}
unzip(zipfile = "Decolonizing_expertise.zip")
```


# Authors

Gabriel Nakamura, Bruno Eleres Soares, Valério D. Pillar, José Alexandre F. Diniz-Filho and Leandro Duarte



